SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
diagnostic performance becomes accuracy - minor change in abstract

  We then categorize and analyze the various defense mechanisms that
  have been developed. Our analysis is based on dimensions such as
  accuracy, performance, deployment and security. Especially notable
  is accuracy, as our findings show that there are
  many defense mechanisms that are tested in a poor manner.
  In addition, we observe that there are many protection mechanisms
  that can be bypassed by attackers that know how the mechanisms
  work. Finally, we see that researchers tend to not make
  their mechanisms available to the community.

@@

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Diagnostic Performance} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
  the overhead of the mechanisms
  that affect the experience of a web user who actually
  uses the protected application.
\item {\it Ease of use} We examine if the protection
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security} We examine how resilient is the system to
  attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus} Based on our exploitation model
  we examine the location where a mechanism detects an attack.
\item {\it Availability} We check if the mechanism and its
  testbed are available on-line.
available 
\end{itemize}

@@

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We find that researchers often test the diagnostic performance
  of their mechanisms poorly. 
\item We also find that researchers do not often make their mechanisms
  available to the community, thus no one can either use their
  mechanism, or replicate their experiments.
\item We discuss how our observations may be the main reasons why the
  mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria for new mechanisms
  and how our work can help researchers to design new countermeasures.
\end{enumerate}

@@

The first two criteria are \emph{Diagnostic Performance} and
\emph{Availability}. The other four criteria are \emph{Computational
  Performance}, \emph{Ease of Use}, \emph{Security}, and
\emph{Detection Locus}.

\subsection{Diagnostic Performance}
\label{ssec:diagnostic-performance}

@@

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Diagnostic Performance and Computational Overhead measurements.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (Locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we will observe), {\sc sql}check has been
extensively tested in terms of diagnostic performance
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

In the case of {\sc xss} attacks that are based on JavaScript or {\sc
  html}, consider a {\sc xor} function that encodes all source of a
web page on the server-side and then, on the client-side, the web
browser decodes the source by applying the same function again (Locus
{\sc x}). Variations of this approach include {\it
  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
randomize the instruction set of {\sc html} and JavaScript
respectively. Contrary to x{\sc js}, in Noncespaces administrators
must set specific policies in a manner similar to a firewall
configuration language. This fact, together with the insufficient
testing of the mechanism (see Table~\ref{tab:comp}) brings up
questions concerning its diagnostic performance. {\it {\sc
    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
JavaScript keywords within the application's legitimate code. This is
done before the processing of an {\sc http} request. When it finds one
it adds a token to it. This results to a ``code mask". Then, before
sending the resulting {\sc html} data to the web user, the framework
searches the data for illegal code by using the same keywords (Locus
{\sc y}). Since all legitimate code has been ``masked", the injected
code can be identified. The pre- and post-processing of the code
though, may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask did not provide measurements
regarding the computational performance of the tool (see
Table~\ref{tab:comp}).

@@

\subsection{Diagnostic Performance}

@@

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
Finally, in the publications that
{\sc amnesia} and {\sc sd}river were presented,
authors managed to break existing application suites
and then test the diagnostic performance of their tools on them.

@@

Notes:
\begin{enumerate}
\item Note that most mechanisms that implement etiological
approaches have not been extensively tested in terms of
diagnostic performance.
\item We need to mention that there are mechanisms that
do not need to be established purely through testing
Since they provide systematic arguments as to why
the design is secure against attacks.
\item Policy enforcement is the
only approach that is
used to prevent {\sc csrf} attacks.
\item See j{\sc csrf} for {\sc soma}'s drawbacks.
\item Discuss about how tools can be easily modified
to detect other attacks ({\sc sql}rand).
\end{enumerate}

>>>>

  We then categorize and analyze the various defense mechanisms that
  have been developed. Our analysis is based on dimensions such as
  accuracy, performance, deployment, security and availability.
  Especially notable is accuracy, as our findings show that there are
  many defense mechanisms that are tested in a poor manner.
  In addition, we observe that there are protection mechanisms
  that can be bypassed by attackers that know how the mechanisms
  work.

@@

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Accuracy} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
  the overhead of the mechanisms
  that affect the experience of a web user who actually
  uses the protected application.
\item {\it Ease of use} We examine if the protection
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security} We examine how resilient is the system to
  attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus} Based on our exploitation model
  we examine the location where a mechanism detects an attack.
\item {\it Availability} We check if the mechanism and its
  testbed are available on-line.
available 
\end{itemize}

@@

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We find that researchers often test the accuracy
  of their mechanisms poorly. 
\item We also find that researchers do not often make their mechanisms
  available to the community, thus no one can either use their
  mechanism, or replicate their experiments.
\item We discuss how our observations may be the main reasons why the
  mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria for new mechanisms
  and how our work can help researchers to design new countermeasures.
\end{enumerate}

@@

The first two criteria are \emph{Accuracy} and
\emph{Availability}. The other four criteria are \emph{Computational
  Performance}, \emph{Ease of Use}, \emph{Security}, and
\emph{Detection Locus}.

\subsection{Accuracy}
\label{ssec:diagnostic-performance}

@@

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Accuracy and Computational Overhead measurements.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.
Both mechanisms that implement this approach,
{\sc sqlg}uard~\cite{BWS05} and
{\sc sql}check~\cite{SW06} are pretty similar
and detect the attack before a query reaches the
database (Locus {\sc z}).
Contrary to {\sc sqlg}uard (and other
mechanisms as we will observe), {\sc sql}check has been
extensively tested in terms of accuracy
as it can be seen in Table~\ref{tab:comp}.
A disadvantage of those mechanisms is that the
application must be modified in every code fragment
that sends an {\sc sql} query to the database for execution.

@@

In the case of {\sc xss} attacks that are based on JavaScript or {\sc
  html}, consider a {\sc xor} function that encodes all source of a
web page on the server-side and then, on the client-side, the web
browser decodes the source by applying the same function again (Locus
{\sc x}). Variations of this approach include {\it
  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
randomize the instruction set of {\sc html} and JavaScript
respectively. Contrary to x{\sc js}, in Noncespaces administrators
must set specific policies in a manner similar to a firewall
configuration language. This fact, together with the insufficient
testing of the mechanism (see Table~\ref{tab:comp}) brings up
questions concerning its accuracy. {\it {\sc
    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
JavaScript keywords within the application's legitimate code. This is
done before the processing of an {\sc http} request. When it finds one
it adds a token to it. This results to a ``code mask". Then, before
sending the resulting {\sc html} data to the web user, the framework
searches the data for illegal code by using the same keywords (Locus
{\sc y}). Since all legitimate code has been ``masked", the injected
code can be identified. The pre- and post-processing of the code
though, may add a significant overhead to the application.
Unfortunately, the authors of {\sc sm}ask did not provide measurements
regarding the computational performance of the tool (see
Table~\ref{tab:comp}).

@@

\subsection{Accuracy}

@@

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
Finally, in the publications that
{\sc amnesia} and {\sc sd}river were presented,
authors managed to break existing application suites
and then test the accuracy of their tools on them.

@@

Notes:
\begin{enumerate}
\item Note that most mechanisms that implement etiological
approaches have not been extensively tested in terms of
accuracy.
\item We need to mention that there are mechanisms that
do not need to be established purely through testing
Since they provide systematic arguments as to why
the design is secure against attacks.
\item Policy enforcement is the
only approach that is
used to prevent {\sc csrf} attacks.
\item See j{\sc csrf} for {\sc soma}'s drawbacks.
\item Discuss about how tools can be easily modified
to detect other attacks ({\sc sql}rand).
\end{enumerate}
